hatchR: A tool set to predict when fish hatch and emerge

### 2025-02-28 inst/poster/hatchR_posterdown/hatchR_posterdown.Rmd
change title and fix Austin et al. error

---
title: "hatchR: A toolset to predict when fish hatch and emerge"
author:
  - name: Morgan Sparks
    affil: 1
  - name: Eli Felts
    affil: 2
  - name: Allison Swartz
    affil: 3
  - name: Bryan Maitland
    affil: 1
affiliation:
  - num: 1
    address: Rocky Mountain Research Station, US Forest Service
  - num: 2
    address: Idaho Fish and Wildlife Conservation Oﬀice, US Fish and Wildlife Service
  - num: 3
    address: College of Forestry, Oregon State University
column_numbers: 4
logoright_name: "./hatchR_posterdown_files/figure-html/agency_logos.png"
logoleft_name: "./hatchR_posterdown_files/figure-html/logo.png"
poster_height: "36in"
poster_width: "48in"
primary_colour: "	#011f4b"
sectitle_bgcol: "#005b96"
sectitle_bordercol: "#005b96"
column_margins: "0.33in"
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

@@

```{r, echo = TRUE}
# get model from model_table
bull_trout_emerge <- model_select(
  author = "Austin et al. 2017",
  species = "bull trout",
  model = "MM",
  development_type = "emerge")

>>>>

---
title: "hatchR: A tool set to predict when fish hatch and emerge"
author:
  - name: Morgan Sparks
    affil: 1
  - name: Eli Felts
    affil: 2
  - name: Allison Swartz
    affil: 3
  - name: Bryan Maitland
    affil: 1
affiliation:
  - num: 1
    address: Rocky Mountain Research Station, US Forest Service
  - num: 2
    address: Idaho Fish and Wildlife Conservation Oﬀice, US Fish and Wildlife Service
  - num: 3
    address: College of Forestry, Oregon State University
column_numbers: 4
logoright_name: "./hatchR_posterdown_files/figure-html/agency_logos.png"
logoleft_name: "./hatchR_posterdown_files/figure-html/logo.png"
poster_height: "36in"
poster_width: "48in"
primary_colour: "	#011f4b"
sectitle_bgcol: "#005b96"
sectitle_bordercol: "#005b96"
column_margins: "0.33in"
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

@@

```{r, echo = TRUE}
# get model from model_table
bull_trout_emerge <- model_select(
  author = "Austin et al. 2019",
  species = "bull trout",
  model = "MM",
  development_type = "emerge")
